Perception of Work Demands and Resources: Does Sheer Volume Matter?

### 2023-02-16 SIOP2023/Counts/counts_poster.Rmd
Made tiny edits to poster

---
title: 'Perception of Work Demands and Resources: Does Sheer Volume Matter?'
author:
  - name: Alicia Stachowski
    affil: 1
  - name: John Kulas
    affil: 2
affiliation:
  - num: 1
    address: University of Wisconsin - Stout
  - num: 2
    address: eRg
column_numbers: 3
primary_colour: "#313ab3"
secondary_colour: "#B4B5B4"
accent_colour: "#FF0000"
logoright_name: 'Stoutlogo_2023.png'
logoleft_name: "erg.png"
output: 
  posterdown::posterdown_html:
    self_contained: false
csl               : "apa7.csl"
bibliography: jobdemands_resources_bibtex.bib
suppress-bibliography: true 
link-citations: true
floatsintext: yes
affiliation_textsize: "50pt"
body_textsize: "50px"
title_textsize:	"75pt"	
author_textsize:	"50pt"
font_family: 'Helvetica'
main_fontfamily: "Helvetica"
#logoleft_name	"Figures/posterdownlogo.png"	Location of the image to use.
#logoright_name	"Figures/posterdownlogo.png"	Location of the image to use.
---

@@

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                 caption = "Focal variable correlations (counts data).",
                 placement = "H",
                 align = c('l','l','l','l','l','l','r','r'),
                 escape = FALSE)

@@

```{r regressiontableeng}
library(papaja)
apa_lm <- apa_print(eng)
apa_table(
  apa_lm$table, 
  caption = "Regression Predicting Engagement.",
  align = c('l','r','r','r','r','r'),
  placement = "H"
)
```

@@

```{r regressiontablestr}
library(papaja)
apa_lm <- apa_print(str)
apa_table(
  apa_lm$table, 
  placement = "H",
  align = c('l','r','r','r','r','r'),
  caption = "Regression Predicting Stress."
)
```

@@

```{r regressiontablebur}
library(papaja)
apa_lm <- apa_print(bur)
apa_table(
  apa_lm$table, 
  placement = "H",
  align = c('l','r','r','r','r','r'),
  caption = "Regression Predicting Burnout."
)
```

@@

## Limitations & Future Directions

Future study could consider additional or other O\*Net items, *kinds* of resources or challenges, additional outcomes (e.g., job satisfaction), or whether volume of resources and demands operationalized in this way are related to other behaviors. Finally, there was a moderate relationship between challenges and hindrances, which may be driven by job complexity – that is, some jobs simply have more elements. With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.

>>>>

---
title: 'Perception of Work Demands and Resources: Does Sheer Volume Matter?'
author:
  - name: Alicia Stachowski
    affil: 1
  - name: John Kulas
    affil: 2
affiliation:
  - num: 1
    address: University of Wisconsin - Stout
  - num: 2
    address: eRg
column_numbers: 3
primary_colour: "#313ab3"
secondary_colour: "#B4B5B4"
accent_colour: "#FF0000"
logoright_name: 'Stoutlogo_2023.png'
logoleft_name: "erg.png"
output: 
  posterdown::posterdown_html:
    self_contained: false
csl               : "apa7.csl"
bibliography: jobdemands_resources_bibtex.bib
suppress-bibliography: true 
link-citations: true
floatsintext: yes
affiliation_textsize: "50pt"
body_textsize: "48px"
title_textsize:	"75pt"	
author_textsize:	"50pt"
font_family: 'Helvetica'
main_fontfamily: "Helvetica"
#logoleft_name	"Figures/posterdownlogo.png"	Location of the image to use.
#logoright_name	"Figures/posterdownlogo.png"	Location of the image to use.
---

@@

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                 caption = "Focal Variable Correlations (Counts Data)",
                 placement = "H",
                 align = c('l','l','l','l','l','l','r','r'),
                 escape = FALSE)

@@

```{r regressiontableeng}
library(papaja)
apa_lm <- apa_print(eng)
apa_table(
  apa_lm$table, 
  caption = "Regression Predicting Engagement",
  align = c('l','r','r','r','r','r'),
  placement = "H"
)
```

@@

```{r regressiontablestr}
library(papaja)
apa_lm <- apa_print(str)
apa_table(
  apa_lm$table, 
  placement = "H",
  align = c('l','r','r','r','r','r'),
  caption = "Regression Predicting Stress"
)
```

@@

```{r regressiontablebur}
library(papaja)
apa_lm <- apa_print(bur)
apa_table(
  apa_lm$table, 
  placement = "H",
  align = c('l','r','r','r','r','r'),
  caption = "Regression Predicting Burnout"
)
```

@@

## Limitations & Future Directions 
Future study could consider additional or other O\*Net items, *kinds* of resources or challenges, additional outcomes (e.g., job satisfaction), or whether volume of resources and demands operationalized in this way are related to other behaviors. Finally, there was a moderate relationship between challenges and hindrances, which may be driven by job complexity. With more job elements comes increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
